Prediction of 2024 US election ...

### 2024-11-02 paper/paper.qmd
update unfinished test simulated data script

# Introduction {#sec-intro}
Election result forecasting has become an essential tool for analysts in political science and the public to predict the outcome of democratic process, such as the presidential election in the United States. Traditionally, individual polls have been used as a snapshot of voter sentiment, but they only reflect temporary changes in the performance of contestants, instead of a precise estimation of the election result. As discussed by @pasek and @blumenthal, the aggregation of multiple polls, or "poll-of-polls," has become a popular technique to reduce individual survey errors and provide more accurate election forecasts. However, the traditional poll aggregation does not reflect dynamics of an election, especially with real-time changes and the introduction of new data. A more adaptable model is required to predict the election result based on both polling data and additional variables, such as historical data and economic indicators.

@@

Further adjustments address polling biases, such as “house effects” (systematic leanings toward a particular candidate) and the mode of polling. Polls from partisan sources are included, but FiveThirtyEight applies a correction to counteract inherent biases [@morris_trump_2024].

>>>>

# Introduction {#sec-intro}
Election result forecasting has become an essential tool for analysts in political science and the public to predict the outcome of democratic process, such as the presidential election in the United States. Traditionally, individual polls have been used as a snapshot of voter sentiment, but they only reflect temporary changes in the performance of contestants, instead of a precise estimation of the election result. As discussed by @pasek and @blumenthal, the aggregation of multiple polls, or "poll-of-polls," has become a popular technique to reduce individual survey errors and provide more accurate election forecasts. However, the traditional poll aggregation does not reflect dynamics of an election, especially with differences in quality of polls. A more adaptable model is required to predict the election result based on both polling data and additional variables, such as sample size and pollster credibility.

@@

Further adjustments address polling biases, such as “house effects” (systematic leanings toward a particular candidate) and the mode of polling. Likely-voter adjustment are applied to all polls of registered voters and adults. Third party adjustment are applied to polls that only consider Biden and Trump as the candidates. Polls from partisan sources are included, but FiveThirtyEight applies a correction to counteract inherent biases [@morris_trump_2024].
